Dynein project log

### 2017-09-30 thesis_stuff/thesis_stuff.tex
Add a good candidate set of run parameters to generate_exploration-data.py

\section{Papers}
\subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}
Yi Qin Gao 2006

>>>>

\section{Papers}
\subsection{Tension on the Linker Gates the ATP-Dependent Release of Dynein from Microtubules - Yildiz 2014}
Yildiz shows that dynein only requires one functional head, and an MTBD linker, to walk. He claims that this shows dynein relies on high bb/ob time, not from communication. He does say that linker tension increases ATP hydrolysis rate, which isn't really inter-head connection.\\
Takeaway: linker tension inhibits MT release. Stepping happens lots when the active head is low-tension (near its partner), but not when it is far away.\\

\subsection{A Simple Theoretical Model Explains Dynein’s Response to Load}
Yi Qin Gao 2006
